HiC Contact Map Comaprison Using Graphlet Approach

### 2018-04-26 papers/manuscripts/manuscript.tex
added graphs

\begin{figure*}
    \centering
    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\textwidth]{figures/orbit-distances_chr14.png}
        \caption{}
        \label{fig:orbit-distances_chr14}
    \end{subfigure}
    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\textwidth]{figures/contact_maps_correlations_chr14.png}
        \caption{}
        \label{fig:contact_maps_correlations_chr14}
    \end{subfigure}
    \caption{   
        \textbf{(a) Pair-wise graphlet signature difference for
        all 276 contact maps:}
        Each point on a graph is the result of averaging all
        the distances across all loci of that contact map.
        ($\bar{\mathbf{d}}^{\scriptscriptstyle A,B}_{i,j} \quad
        \forall i,j \in \{1 ... 23\} \quad \& \quad j \ge i$).  
        \vspace{.1cm} \\
        \textbf{(b) pair-wise average contact map orbit correlations
         for all contact maps:}
        ($\bar{\mathbf{m}}^{\scriptscriptstyle \scriptscriptstyle A,B}_{i,j} 
        \quad \forall i,j \in \{1 ... 23\} \quad \& \quad j \ge i$:
        average along the red \textit{vertical} arrow in figure 
        \ref{graphlet_correlation_schema}).
        These values are calculated by averaging over 
        pairwise correlations of orbits of
        $\mathbb{Q}$ in a contact map.
     }
    \label{fig:results_all}
\end{figure*}

@@

This approach also allows for comparison of orbits
themsleves. By comparing average oribit correlations
across all contact maps of two cell lines, we can
have a measure of how similar certain orbits are
between cell lines. This can give us a 
\textit{global} measure
of how similar two cell lines are in terms of 
\textit{local} spatial positionings.
Figure \ref{fig:orbits_correlations_all} 
demonstrates average correlations across all 72 orbits within each contact map.
Figure \ref{fig:orbits_correlations_all} clearly illustrates certain
orbits of Leukemic have higher correlation to each other than to the
normal MIT cell. In fact our statistical analysis shows that 
\textit {for orbits in $\mathbb{Q}$, 
intra-leukemic orbit correlations are significantly higher
than leukemic-normal orbit correlations}. This implies
there are significant differences between normal and
leukemic cells in terms of their local structure.

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/orbits_correlations_all.png}
    \caption{
        \textbf{Pair-wise average orbit correlations:}
        In figure \ref{fig:orbits_correlations_all}, each point
        in the graph is the result of averaging pair-wise
        orbit correlations over all contact maps
        ($\frac{1}{276}\sum_{i=0}^{23}\sum_{j=i}^{23}{
        m^{\scriptscriptstyle \scriptscriptstyle A,B}_{i,j, o}} \quad 
        \forall o \in \{0, 1, ..., 72\}$:
        average along the red \textit{horizontal} arrows in figure 
        \ref{graphlet_correlation_schema}).
        Counts for certain orbits are always zero in inter-chromosomal
        maps, leading to average value close to zero in 
        Figure \ref{fig:orbits_correlations_all}.
        In this figure, cancer cells data points are depicted
        in warm colors while normal cells are depicted in
        cold colors in increased contrast. As can be seen
        orbit distributions are more similar to each other
        for cancer cells.
    }
    \label{fig:orbits_correlations_all}
\end{figure*}

>>>>

\begin{figure*}
    \centering
    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\textwidth]{figures/orbit-distances_chr14.png}
    \end{subfigure}
    \caption{   
        \textbf{Pair-wise graphlet signature difference for
        all 276 contact maps:}
        Each point on a graph is the result of averaging all
        the distances across all loci of that contact map.
        ($\bar{\mathbf{d}}^{\scriptscriptstyle A,B}_{i,j} \quad
        \forall i,j \in \{1 ... 23\} \quad \& \quad j \ge i$).  
     }
    \label{fig:results_all}
\end{figure*}

@@

This approach also allows for comparison of orbits
themsleves. By comparing average oribit correlations
across all contact maps of two cell lines, we can
have a measure of how similar certain orbits are
between cell lines. This can give us a 
\textit{global} measure
of how similar two cell lines are in terms of 
\textit{local} spatial positionings.
Figure \ref{fig:orbits_correlations_all} 
demonstrates average correlations across all 72 orbits within each contact map.
Figure \ref{fig:orbits_correlations_all} clearly illustrates certain
orbits of Leukemic have higher correlation to each other than to the
normal MIT cell. In fact our statistical analysis shows that 
\textit {for orbits in $\mathbb{Q}$, 
intra-leukemic orbit correlations are significantly higher
than leukemic-normal orbit correlations}. This implies
there are significant differences between normal and
leukemic cells in terms of their local structure.
\begin{figure*}
    \centering
    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\textwidth]{figures/contact_maps_correlations_cancer_vs_normal.png}
    \end{subfigure}
    \caption{
        \textbf{Pair-wise 
        average contact map orbit correlations
        for all contact maps:}
        ($\bar{\mathbf{m}}^{\scriptscriptstyle \scriptscriptstyle A,B}_{i,j} 
        \quad \forall i,j \in \{1 ... 23\} \quad \& \quad j \ge i$:
        average along the 
        red \textit{vertical} arrow in figure 
        \ref{graphlet_correlation_schema}).
        These values are calculated by averaging over 
        pairwise correlations of orbits of
        $\mathbb{Q}$ in a contact map.
}
    \label{fig:contact_map_correlations_all}
\end{figure*}

\begin{figure*}
    \centering
    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\textwidth]{figures/orbits_correlations_cancer_vs_normal.png}
    \end{subfigure}
    \begin{subfigure}[b]{\textwidth}
    \includegraphics[width=\textwidth]{figures/orbits_correlations_all.png}
    \end{subfigure}
    \caption{
        \textbf{Pair-wise average orbit correlations:}
        In figure \ref{fig:orbits_correlations_all}, each point
        in the graph is the result of averaging pair-wise
        orbit correlations over all contact maps
        ($\frac{1}{276}\sum_{i=0}^{23}\sum_{j=i}^{23}{
        m^{\scriptscriptstyle \scriptscriptstyle A,B}_{i,j, o}} \quad 
        \forall o \in \{0, 1, ..., 72\}$:
        average along the red \textit{horizontal} arrows in figure 
        \ref{graphlet_correlation_schema}).
        Counts for certain orbits are always zero in inter-chromosomal
        maps, leading to average value close to zero in 
        Figure \ref{fig:orbits_correlations_all}.
        In this figure, cancer cells data points are depicted
        in warm colors while normal cells are depicted in
        cold colors in increased contrast. As can be seen
        orbit distributions are more similar to each other
        for cancer cells.
    }
    \label{fig:orbits_correlations_all}
\end{figure*}
